\documentclass{report}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{background}
\usetikzlibrary{calc}

\backgroundsetup{
  scale=1,
  angle=0,
  opacity=1,
  contents={
    \begin{tikzpicture}[remember picture, overlay]
      \draw [line width=1pt]
        ($(current page.north west) + (1cm,-1cm)$)
        rectangle
        ($(current page.south east) + (-1cm,1cm)$);
    \end{tikzpicture}
  }
}
% Page geometry
\geometry{a4paper, margin=1in}

% Title formatting
\titleformat{\chapter}[display]
{\normalfont\huge\bfseries}{\chaptertitlename\ \thechapter}{20pt}{\Huge}
\titlespacing*{\chapter}{0pt}{50pt}{40pt}

% Code listing style
\lstset{
  basicstyle=\ttfamily\small,
  breaklines=true,
  frame=single,
  commentstyle=\color{green!50!black},
  keywordstyle=\color{blue},
  stringstyle=\color{red},
  numbers=left,
  numberstyle=\tiny\color{gray},
  numbersep=5pt
}

% Header and footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{ONLINE BANKING SYSTEM}
\fancyhead[R]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

\lstdefinelanguage{JavaScript}{
  keywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break},
  keywordstyle=\color{blue}\bfseries,
  ndkeywords={class, export, boolean, throw, implements, import, this},
  ndkeywordstyle=\color{darkgray}\bfseries,
  identifierstyle=\color{black},
  sensitive=false,
  comment=[l]{//},
  morecomment=[s]{/*}{*/},
  commentstyle=\color{purple}\ttfamily,
  stringstyle=\color{red}\ttfamily,
  morestring=[b]',
  morestring=[b]"
}

% Document begins
\begin{document}

\begin{titlepage}
\centering
{\LARGE\bfseries WT PROJECT REPORT\par}
\vspace{1cm}
{\huge\bfseries ONLINE BANKING SYSTEM\par}
\vspace{1.5cm}
{\Large Bachelor of Technology\par}
\vspace{0.5cm}
{\Large In\par}
\vspace{0.5cm}
{\Large Computer Science and Engineering\par}
\vspace{1.5cm}
{\Large Under esteemed Guidance of\par}
\vspace{0.5cm}
{\Large Mrs. Venkata Ratnam\par}
{\Large Asst. Professor, Dept. of CSE\par}
\vspace{1.5cm}
{\Large\bfseries DEPARTMENT OF COMPUTER SCIENCE\\AND ENGINEERING\par}
\vspace{0.5cm}
{\Large\bfseries ANIL NEERUKONDA INSTITUTE OF\\TECHNOLOGY AND SCIENCES\par}
\vspace{0.5cm}
{\Large\bfseries SANGIVALASA, VISAKHAPATNAM\par}
\end{titlepage}

\chapter*{PROJECT TITLE: ONLINE BANKING SYSTEM}

\section*{Team members:}
\begin{tabular}{|l|l|}
\hline
\textbf{Name of the Student} & \textbf{Roll No} \\
\hline
K.Akhila & A21126510095 \\
\hline
R.Sai Ashish & A21126510115 \\
\hline
B.Pujitha & A21126510073 \\
\hline
B.Govinda Rao & A21126510071 \\
\hline
S.Raju & A21126510209 \\
\hline
\end{tabular}

\chapter*{Bonafide Certificate}
This is to certify that this project report ``Online Banking System'' is the Bonafede
work of K Akhila A21126510095, R Sai Ashish A21126510115, B Pujitha
A21126510073, B Govinda Rao A21126510071 and S Raju A21126510209. This
project is carried out and is submitted in the partial fulfillment of the requirements for
the award of BACHELOR OF TECHNOLOGY in Computer Science and
Engineering, under Anil Neerukonda Institute of Technology and Sciences during the
academic year 2023- 2024.

\vspace{1cm}
\noindent\begin{tabular}{lr}
\textbf{Head of the Department} & \textbf{Project Guide} \\
Prof.M.Ramakrishna Murty & Mrs. K.Venkataratnam \\
(Professor \& HOD) & (Asst.Professor) \\
Department of CSE & Department of CSE \\
ANITS & ANITS
\end{tabular}

\chapter*{Declaration}
This is to certify that the project work entitled ``Online Banking System'' is a
Bonafide work carried out by as a part of BTech 3$^{rd}$ year 2$^{nd}$ semester of Computer
Science and Engineering of Anil Neerukonda Institute of Technology and Sciences,
Visakhapatnam during the academic year 2023-2024.

We are K Akhila, R Sai Ashish, B Pujitha, B Govinda Rao and S Raju of 3rd year
B.Tech, Department of Computer Science and Engineering from ANITS,
Visakhapatnam, hereby declare that the project work entitled ``Online Banking
System'' is carried out by us and is submitted in the fulfillment of the requirement for
the award of Bachelor of Technology in Computer Science and Engineering, under
Anil Neerukonda Institute of Technology and Sciences during the academic year
2023-2024 has not been submitted to any other university for the award of any kind of
degree.

\vspace{1cm}
\noindent\begin{tabular}{ll}
\textbf{Name} & \textbf{Reg.No} \\
K. AKHILA & A21126510095 \\
R. SAI ASHISH & A21126510115 \\
B. PUJITHA & A21126510073 \\
B. GOVINDA RAO & A21126510071 \\
S. RAJU & A21126510209
\end{tabular}

\chapter*{Acknowledgement}
The satisfaction that accompanies the successful completion of any task would be
incomplete without mentioning the people who made it possible, and whose constant
guidance and encouragement always upheld the morale. We take a great pleasure in
presenting a project, which is the result of a studied blend of both research and
knowledge.

We first take the privilege to thank our Head of the department Prof M.
RAMAKRISHNA MURTHY, for permitting us in laying the first stone of success.
We feel grateful to thank MRS. K. VENKATA RATNAM Madam, who is our project
guide and who shared her valuable knowledge with us and made us understand the
real essence of the topic and created interest in us to put our continuous efforts in the
project.

\vspace{1cm}
\noindent\begin{tabular}{ll}
\textbf{Name} & \textbf{Reg.No} \\
K. AKHILA & A21126510095 \\
R. SAI ASHISH & A21126510115 \\
B. PUJITHA & A21126510073 \\
B. GOVINDA RAO & A21126510071 \\
S. RAJU & A21126510209
\end{tabular}

\tableofcontents

\chapter{Project Abstract}
The proliferation of online banking has revolutionized the way financial transactions are
conducted, offering unparalleled convenience and accessibility. However, with this
convenience comes the challenge of ensuring robust security measures to protect sensitive
financial data and prevent unauthorized access.

This project aims to address these challenges by proposing innovative solutions to enhance
both security and user experience in online banking systems.

The project will begin with a comprehensive analysis of existing security protocols and user
interface designs in online banking systems. This analysis will identify potential
vulnerabilities and areas for improvement. Subsequently, the project will focus on the
development and implementation of advanced security measures such as multi-factor
authentication, encryption techniques, and real-time fraud detection algorithms.

Additionally, user-centric design principles will be employed to create intuitive and user-friendly 
interfaces that enhance the overall banking experience.

The effectiveness of the proposed solutions will be evaluated through rigorous testing
procedures, including simulated cyber-attacks and user feedback surveys. Furthermore, the
project will explore the integration of emerging technologies such as biometrics and
blockchain to further enhance security and streamline transactions.

By the conclusion of this project, we anticipate significant advancements in the security and
usability of online banking systems. These advancements will not only bolster consumer
trust and confidence but also contribute to the continued growth and evolution of digital
banking services in an increasingly interconnected world.

\chapter{Objectives}
Here are a few objectives for your Online Banking System project:

\begin{enumerate}
\item \textbf{Security Analysis:} Conduct a comprehensive review of online banking security
protocols and user interface designs, identifying vulnerabilities and proposing
enhancements for robust protection of sensitive financial data.

\item \textbf{Advanced Security Measures:} Implement state-of-the-art security technologies,
including multi-factor authentication and encryption algorithms, to fortify online
banking systems against cyber threats and ensure the integrity of financial
transactions.

\item \textbf{User-Centric Design:} Employ user-centric design principles to create intuitive
and accessible interfaces for online banking, enhancing the user experience and
facilitating seamless navigation for customers of diverse demographics.

\item \textbf{Solution Evaluation:} Rigorously test implemented security measures through
simulated cyber-attacks and user feedback surveys to assess effectiveness in
safeguarding online banking systems and building consumer trust.

\item \textbf{Integration of Emerging Technologies:} Explore the integration of emerging
technologies like biometrics and blockchain to further enhance security and
streamline transactions in online banking, anticipating future challenges and
advancements in the digital finance landscape.

\item \textbf{Trust and Confidence Measurement:} Measure the impact of security solutions
on consumer trust and confidence in online banking services, utilizing perception
studies and trust metrics to ensure transparency and reliability in financial
transactions.

\item \textbf{Contribution to Digital Banking Evolution:} Drive innovation and set new
standards for security and user experience in online banking, contributing to the
continued growth and evolution of digital banking services in an increasingly
interconnected world.
\end{enumerate}

\chapter{Software \& Modules Used}
\begin{enumerate}
\item \textbf{Node.js and npm:}
Ensure Node.js is installed on your system, which includes npm.

\item \textbf{Express.js:}
Install Express.js using npm to create a web application framework.

\item \textbf{EJS (Embedded JavaScript):}
Install EJS using npm for embedding JavaScript code within HTML pages.

\item \textbf{PHPMyAdmin:}
\begin{itemize}
\item Set up a server environment with PHP and MySQL installed.
\item Access PHPMyAdmin through a web browser for database management.
\end{itemize}

\item \textbf{Connecting to MySQL Database:}
Install the MySQL module for Node.js using npm for connecting Express.js
with MySQL databases.

\item \textbf{Setting Up Routes and Views:}
\begin{itemize}
\item Create routes in Express.js to handle HTTP requests and responses.
\item Configure EJS views for rendering dynamic HTML content.
\end{itemize}

\item \textbf{Code Editor (Visual Studio Code):}
\begin{itemize}
\item Utilize Visual Studio Code as the code editor for project development
and editing.
\end{itemize}
\end{enumerate}

\section*{Installation Steps:}
\begin{enumerate}
\item \textbf{Install Node.js and npm:}
\begin{itemize}
\item Download and install Node.js from the official website.
\item npm will be installed along with Node.js.
\end{itemize}

\item \textbf{Install Express.js:}
\begin{itemize}
\item Open a terminal/command prompt and
run: \texttt{npm install express}
\end{itemize}

\item \textbf{Install EJS:}
\begin{itemize}
\item Run the following command in the terminal/command prompt:
\texttt{npm install ejs}
\end{itemize}

\item \textbf{Set Up PHPMyAdmin:}
\begin{itemize}
\item Install a server environment like XAMPP or WAMP, which
includes PHPMyAdmin, or install PHPMyAdmin separately.
\item Create necessary databases and tables for the project in PHPMyAdmin.
\end{itemize}

\item \textbf{Connecting to MySQL Database:}
\begin{itemize}
\item Install the MySQL module for Node.js:
\texttt{npm install mysql}
\end{itemize}
\end{enumerate}

\chapter{Structure of the Project}
% Placeholder for project structure diagram or description
[Project structure diagram would be inserted here]

\chapter{Interface and Implementation}

\section{app.js}
\begin{lstlisting}[language=JavaScript]
// Main application code (Node.js/Express)
// Code that initializes the server, sets up database connections,
// defines routes, and implements session management
\end{lstlisting}

\section{Account.ejs}
\begin{lstlisting}[language=HTML]
<!-- HTML template for account creation page with CSS styling -->
\end{lstlisting}

\section{success.ejs}
\begin{lstlisting}[language=HTML]
<!-- HTML template for success message after account creation -->
\end{lstlisting}

\section{login.ejs}
\begin{lstlisting}[language=HTML]
<!-- HTML template for user login page with CSS styling -->
\end{lstlisting}

\section{login\_success.ejs}
\begin{lstlisting}[language=HTML]
<!-- HTML template for successful login with user details display -->
\end{lstlisting}

\section{Transaction.ejs}
\begin{lstlisting}[language=HTML]
<!-- HTML template for transaction page with form elements -->
\end{lstlisting}

\section{Transaction\_details.ejs}
\begin{lstlisting}[language=HTML]
<!-- HTML template for viewing transaction details -->
\end{lstlisting}

\section{Transaction\_success.ejs}
\begin{lstlisting}[language=HTML]
<!-- HTML template for transaction success/failure messages -->
\end{lstlisting}

\section{admin.ejs}
\begin{lstlisting}[language=HTML]
<!-- HTML template for admin login page -->
\end{lstlisting}

\section{admin\_success.ejs}
\begin{lstlisting}[language=HTML]
<!-- HTML template for admin dashboard after successful login -->
\end{lstlisting}

\section{customer\_details.ejs}
\begin{lstlisting}[language=HTML]
<!-- HTML template for displaying customer information to admin -->
\end{lstlisting}

\section{transaction\_details.ejs}
\begin{lstlisting}[language=HTML]
<!-- HTML template for displaying transaction history to admin -->
\end{lstlisting}

\section{Header.ejs}
\begin{lstlisting}[language=HTML]
<!-- Reusable header template with navigation -->
\end{lstlisting}

\section{Footer.ejs}
\begin{lstlisting}[language=HTML]
<!-- Reusable footer template with contact information -->
\end{lstlisting}

\chapter{Outputs}
\section*{Home Page:}
% Placeholder for screenshot
[Screenshot of home page]

\section*{User Sign up:}
% Placeholder for screenshot
[Screenshot of user sign up page]

\section*{User Account Login:}
% Placeholder for screenshot
[Screenshot of user login page]

\section*{Transaction:}
% Placeholder for screenshot
[Screenshot of transaction page]

\section*{Transaction with insufficient money:}
% Placeholder for screenshot
[Screenshot of insufficient funds error]

\section*{Admin login:}
% Placeholder for screenshot
[Screenshot of admin login page]

\section*{Admin Monitoring Customer Details:}
% Placeholder for screenshot
[Screenshot of customer details admin view]

\section*{Admin Monitoring Customer Transactions:}
% Placeholder for screenshot
[Screenshot of transaction details admin view]

\chapter{References}
\begin{itemize}
\item \url{https://stackoverflow.com/questions/5132923/how-to-add-a-primary-key-to-a-mysql-table}
\item \url{https://stackoverflow.com/questions/11794659/sql-script-how-to-write-alter-statements-to-set-primary-key-on-an-existing-tabl}
\item \url{https://stackoverflow.com/questions/9070764/insert-auto-increment-primary-key-to-existing-table}
\item \url{https://stackoverflow.com/questions/5813771/in-ejs-template-engine-how-do-i-include-a-footer}
\item \url{https://stackoverflow.com/questions/22212440/using-math-class-to-convert-cosine-into-degrees}
\item \url{https://www.google.com/amp/s/www.geeksforgeeks.org/how-to-connect-node-js-application-to-mysql/amp/}
\item \url{https://stackoverflow.com/questions/13396119/how-to-add-a-value-to-existing-value-using-sql-query}
\end{itemize}

\end{document}